\chapter{Autres}
\cat{Alexandre Chatnotte}{chatnotte}{placeholder. lore goes here}
\cat{Chauveteur}{chauveteur}{placeholder. lore goes here}
\cat{Chat de Kefan}{kefan}{placeholder. lore goes here}
\cat{Chat de base}{default}{placeholder. lore goes here}
\cat{Chouvrier}{chouvrier}{placeholder. lore goes here}
\cat{Poisson chat}{catfish}{placeholder. lore goes here}
\cat{Chatvalier}{chatvalier}{placeholder. lore goes here}
\cat{Little kitten}{littlekitten}{placeholder. lore goes here}
\cat{Pipe chat}{pipechat}{placeholder. lore goes here}
\cat{Chatromatique}{chatromatique}{placeholder. lore goes here}
\cat{Choeuf}{choeuf}{placeholder. lore goes here}
\cat{Chat magnetique}{chatmagnetique}{placeholder. lore goes here}
\cat{Chatdolf Chitler}{chatdolfchitler}{placeholder. lore goes here}
\cat{Mc Chat}{mcchat}{placeholder. lore goes here}
\cat{Chatrl Marx}{chatrlmarx}{placeholder. lore goes here}
\cat{Chatramide}{chatramide}{placeholder. lore goes here}
\cat{Chatlemagne}{chatrlemagn}{placeholder. lore goes here}
\cat{Force chatripette}{forcechatripette}{placeholder. lore goes here}
\cat{Chortes}{chortes}{placeholder. lore goes here}
\cat{Chatlade}{chatlade}{placeholder. lore goes here}
\cat{Chatpoleon Bonaparte}{chatpoleon}{placeholder. lore goes here}
\cat{Chatzene}{chatzene}{placeholder. lore goes here}
\cat{Chesus Chat}{chesus}{placeholder. lore goes here}
\cat{Chat d'assault}{chatdassault}{placeholder. lore goes here}
\cat{Angrycat}{angrycat}{placeholder. lore goes here}
\cat{Chatlut}{chatlut}{placeholder. lore goes here}
\cat{Yari Chatshigaru}{yarichatshigaru}{placeholder. lore goes here}
\cat{Chatrfield}{chatrfield}{placeholder. lore goes here}
\cat{Mousquechat}{mousquechat}{placeholder. lore goes here}
\newpage
